---
output: github_document
---


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# microsynth

The goal of microsynth is to implement the synthetic control method for micro-level data as outlined in Robbins, Saunders, and Kilmer (2017). \code{microsynth} is designed for use
in assessment of the effect of an intervention using longitudinal data.
However, it may also be used to calculate propensity score-type weights in
cross-sectional data. \code{microsynth} is a generalization
of \code{Synth} (see Abadie and Gardeazabal (2003) and Abadie, Diamond,
Hainmueller (2010, 2011, 2014)) that is designed for data at a more granular
level (e.g., micro-level). For more details see the help vignette:
\code{vignette('microsynth', package = 'microsynth')}.

## Installation

You can install microsynth from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("ssdavenport/microsynth")
```

## Example

This is a basic example which shows you how to run a simple microsynth model, using block-level panel data to evaluate a crime intervention:

```{r example}
library("microsynth")
# Use seattledmi, block-level panel data, to evaluate a crime intervention.

# Declare time-variant (outcome) and time-invariant variables for matching
cov.var <- c('TotalPop', 'BLACK', 'HISPANIC', 'Males_1521',
       'HOUSEHOLDS', 'FAMILYHOUS', 'FEMALE_HOU', 'RENTER_HOU', 'VACANT_HOU')


match.out <- c('i_felony', 'i_misdemea', 'i_drugs', 'any_crime')

set.seed(99199) # for reproducibility

# Perform matching and estimation, without permutations or jackknife
# runtime: < 1 min
sea1 <- microsynth(seattledmi,
                  idvar="ID", timevar="time", intvar="Intervention",
                  start.pre=1, end.pre=12, end.post=16,
                  match.out=match.out, match.covar=cov.var,
                  result.var=match.out, omnibus.var=match.out,
                  test="lower")

sea1 # View description of microsynth object and results

```
